Nail: A practical interface generator for data formats

### 2014-04-30 paper/osdi14/eval.tex
two more subsubsections
mostly misc fmt stuff

\paragraph{DNS.}

\input{fig-dnsfull}
Domain Name System(DNS) packets are described in RFC 1035 and our grammar almost directly
corresponds to the diagrams in Section 4 of that document. Each DNS packet consists of a header, a
set of question records and a set of answer records. Domain names in both queries and answers are
encoded as a sequence of Pascal-style strings. Each label is preceded by a length field, and the
domain name is terminated by a $0$ octet. The client's query packet contains one question
record to the server for each DNS look-up it wants to perform. In addition to the appropriate
response records, the server's reply contains a duplicate of the client's question section, which
allows stateless DNS clients and caches.

@@

\paragraph{Ethernet}
\XXX[TODO]
\subsubsection{ZIP Files.}
\input{fig-zip}
\label{s:eval-format-zip}
Another particularly tricky file format is the ZIP compressed archive format\cite{pkzip}.
ZIP files are normally parsed end-to-beginning. At the end of each ZIP file is an \emph{end-of-directory
header}. This header contains a variable length comment, so it has to be located by scanning
backwards from the end of the file until a magic number and a valid length field is found. Many ZIP
implementations disagree on how to find this header in confusing situations, such as when the
comment contains the valid magic bytes\cite{wolf-berlinsides-zip}.
This end-of-directory header contains the offset and size of the \emph{ZIP directory}, which is an
array of one \emph{directory entry header} per file in the archive.
Each entry stores file meta data, such as file name, compressed and uncompressed size and a checksum,
in addition to the offset of a \emph{local file header}. The local file header duplicates most
information from the directory entry header and the compressed file contents follow it immediately.

@@

Our ZIP grammar is a good example of transformations can capture complicated syntax in real-world
file format. The \texttt{zip\_file} grammar first splits the entire file stream into two streams
based on the \texttt{zip\_end\_of\_directory} transform.
\texttt{zip\_end\_of\_directory_parse(NailStream *files, NailStream *dir, NailStream (current))}
finds the end of directory header as described above by scanning the file backwards and splits the
file into two streams, one containing the end-of-directory header and one containing the file
contents. The header stream is then parsed. The file stream, to which all the offsets in the
metadata refer, is passed as an argument to the \texttt{end\_of\_directory} parser.
The directory header is then parsed and the offset and size transforms provided with Nail are used
to isolate the actual directory from the file stream. Each directory entry in turn points to a local
file header.

The \texttt{file} grammar for a zip file entry is particularly interesting. It receives the file
size, checksum and compression method of the file from the directory header. However, this same
information is duplicated in the file entry, so the grammar uses a standard \texttt{depend}
transform to check whether the two values are equal. Unlike most other transforms, \texttt{depend}
does not consume or produce strings, it only checks that two dependent fields are equal when parsing
and assigns the value of the second field to the first when generating. Immediately following the
file entry is the compressed data. Because most compression algorithms operate on unbounded streams
of data, Nail decompresses data in two steps.
First, it isolates the compressed data from the rest of the stream by using the size transform. In
this case, size operates on the current stream, which means it will consume data starting at the
current position of the parser in the input.
Second, Nail invokes a custom transform that implements the appropriate compression and decompression
functions based on the specified compression method. These functions are otherwise oblivious about
the layout or metadata of the file.

@@

Our DNS grammar, which is partly reproduced in Figure~\ref{fig:dns-full} consists of a 48 line  Nail
grammar and 64 lines of C implementing DNS label compression.
The grammar describes both the structure of DNS packets (36 lines) and of a simple zone-file format
(16 lines) supporting A, NS, MX and CNAME records.

With this grammar, we built a simple authoritative DNS server, which parses a zone file, listens to incoming DNS
requests, parses them and generates appropriate responses, is implemented in 183 lines of C. The
same grammar is used, together with 98 lines of C, to implement a minimal clone of the
\texttt{host} command-line tool. Most of this code consists of a custom hashtable and system
interface code, such as listening to sockets and reading the zonefile.

@@

However, the closest in functionality and intent is Dan Bernstein's
djbdns,\footnote{\url{http://cr.yp.to/djbdns.html}} which aims to be
a minimalist, highly secure DNS server. The latest release of djbdns,
including various support tools, is about 10,000 lines of C as measured by
\texttt{sloccount}. \XXX[Show that we only count the DNS server parts, not the rest. List some
features we don't have]

@@

Finally, we used the \texttt{queryperf} tool provided with BIND to query each domain between zero
and three times on a local instance of BIND or NailDNS. Both DNS servers were operating on a single, 
core  of an Intel i7-3610QM with 12GB of RAM on an idle system, and the benchmark tool kept at most 20
queries outstanding at once. The queryperf tool was configured to
repeat the same, randomised sequence of queries for one minute and the average throughput and
response latency were measured.  We repeated each test seven times  with 50.000
domain names, restarting each daemon in between. We also performed one initial dry run to warm the
file system cache for the zone file. We repeated the tests with 1 million domain names and found
that the servers performed almost identically.

>>>>

\subsubsection{DNS.}

\input{fig-dnsfull}

\begin{figure}
\smaller[0.5]
\input{code/dns-xform}
\caption{Signatures of stream transform functions for handling DNS label compression.}
\label{fig:dns-xform}
\end{figure}

Domain Name System(DNS) packets are described in RFC 1035 and our grammar almost directly
corresponds to the diagrams in Section 4 of that document. Each DNS packet consists of a header, a
set of question records and a set of answer records. Domain names in both queries and answers are
encoded as a sequence of Pascal-style strings. Each label is preceded by a length field, and the
domain name is terminated by a $0$ octet. The client's query packet contains one question
record to the server for each DNS look-up it wants to perform. In addition to the appropriate
response records, the server's reply contains a duplicate of the client's question section, which
allows stateless DNS clients and caches.

@@

\subsubsection{Ethernet}
\XXX[TODO]
\subsubsection{ZIP Files.}
\input{fig-zip}
\label{s:eval-format-zip}
Another particularly tricky file format is the ZIP compressed archive format\cite{pkzip}.
ZIP files are normally parsed end-to-beginning. At the end of each ZIP file is an \emph{end-of-directory
header}. This header contains a variable length comment, so it has to be located by scanning
backwards from the end of the file until a magic number and a valid length field is found. Many ZIP
implementations disagree on how to find this header in confusing situations, such as when the
comment contains the valid magic bytes\cite{wolf-berlinsides-zip}.
This end-of-directory header contains the offset and size of the \emph{ZIP directory}, which is an
array of one \emph{directory entry header} per file in the archive.
Each entry stores file meta data, such as file name, compressed and uncompressed size and a checksum,
in addition to the offset of a \emph{local file header}. The local file header duplicates most
information from the directory entry header and the compressed file contents follow it immediately.

@@

Our ZIP grammar is a good example of transformations can capture complicated syntax in real-world
file format. The \cc{zip\_file} grammar first splits the entire file stream into two streams
based on the \cc{zip\_end\_of\_directory} transform.
\cc{zip\_end\_of\_directory_parse(NailStream *files, NailStream *dir, NailStream (current))}
finds the end of directory header as described above by scanning the file backwards and splits the
file into two streams, one containing the end-of-directory header and one containing the file
contents. The header stream is then parsed. The file stream, to which all the offsets in the
metadata refer, is passed as an argument to the \cc{end\_of\_directory} parser.
The directory header is then parsed and the offset and size transforms provided with Nail are used
to isolate the actual directory from the file stream. Each directory entry in turn points to a local
file header.

The \cc{file} grammar for a zip file entry is particularly interesting. It receives the file
size, checksum and compression method of the file from the directory header. However, this same
information is duplicated in the file entry, so the grammar uses a standard \cc{depend}
transform to check whether the two values are equal. Unlike most other transforms, \cc{depend}
does not consume or produce strings, it only checks that two dependent fields are equal when parsing
and assigns the value of the second field to the first when generating. Immediately following the
file entry is the compressed data. Because most compression algorithms operate on unbounded streams
of data, Nail decompresses data in two steps.
First, it isolates the compressed data from the rest of the stream by using the size transform. In
this case, size operates on the current stream, which means it will consume data starting at the
current position of the parser in the input.
Second, Nail invokes a custom transform that implements the appropriate compression and decompression
functions based on the specified compression method. These functions are otherwise oblivious about
the layout or metadata of the file.

@@

Our DNS grammar, which is partly reproduced in Figure~\ref{fig:dns-full}, consists of a 48 line Nail
grammar and 64 lines of C implementing DNS label compression, whose signatures are shown in
Figure~\ref{fig:dns-xform}.
The grammar describes both the structure of DNS packets (36 lines) and of a simple zone-file format
(16 lines) supporting A, NS, MX and CNAME records.

With this grammar, we built a simple authoritative DNS server, which parses a zone file, listens to incoming DNS
requests, parses them and generates appropriate responses, is implemented in 183 lines of C. The
same grammar is used, together with 98 lines of C, to implement a minimal clone of the
\cc{host} command-line tool. Most of this code consists of a custom hashtable and system
interface code, such as listening to sockets and reading the zonefile.

@@

However, the closest in functionality and intent is Dan Bernstein's
djbdns,\footnote{\url{http://cr.yp.to/djbdns.html}} which aims to be
a minimalist, highly secure DNS server. The latest release of djbdns,
including various support tools, is about 10,000 lines of C as measured by
\cc{sloccount}. \XXX[Show that we only count the DNS server parts, not the rest. List some
features we don't have]

@@

Finally, we used the \cc{queryperf} tool provided with BIND to query each domain between zero
and three times on a local instance of BIND or NailDNS. Both DNS servers were operating on a single, 
core  of an Intel i7-3610QM with 12GB of RAM on an idle system, and the benchmark tool kept at most 20
queries outstanding at once. The queryperf tool was configured to
repeat the same, randomised sequence of queries for one minute and the average throughput and
response latency were measured.  We repeated each test seven times  with 50.000
domain names, restarting each daemon in between. We also performed one initial dry run to warm the
file system cache for the zone file. We repeated the tests with 1 million domain names and found
that the servers performed almost identically.
